Data getter for peekbank analysis

### 2025-03-20 1_get_data.qmd

```{r}
load(file = here("..", "peekbank-method", "cached_intermediates", "1_d_aoi.Rds"))
```

>>>>

```{r}
load(file = here("..", "peekbank-method", "cached_intermediates", "1_d_aoi.Rds"))
#cache this here as an interim hack until we bring in the full pipeline
saveRDS(d_aoi, here("cached_intermediates","1_d_aoi.Rds"))
```
